Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-18 main.tex
Some responses - still thinking about the X-policy part

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep hyperproperty
where: \bcp{Which parts of this are common to {\em all} contoured lockstep
  hyperproperties (i.e., which should be part of the definition of contoured
  lockstep hyperproperties) and which are specific to (nested) NI?}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, \bcp{where $n$ is the length of the traces,} the
  pair of truncated traces $\overline{(C, 
    M)}_m$ and $\overline{(C, M')}_m$ is also in the set if $m < n$ \bcp{or
    $n = \infty$}.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.
\end{itemize}

\leo{..and the observations of each trace coincide, right?}\bcp{Yes, I guess
  so.}

\bcp{It feels like something is missing here: This definition seems to be
  requiring that secret data never affect observations, but our tester is
  ensuring something more: that inaccessible locations are not {\em changed}
(at least without also changing their tag to make them accessible).  Where
is that condition being imposed?}

>>>>

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep hyperproperty
where: \bcp{Which parts of this are common to {\em all} contoured lockstep
  hyperproperties (i.e., which should be part of the definition of contoured
  lockstep hyperproperties) and which are specific to (nested) NI?}
\leo{I'd say contoured lockstep hyperproperties are as above - and the following are
  the generalization for nested ones.}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, \bcp{where $n$ is the length of the traces,}\leo{Yes I put that in the definition of traces above, but we could repeat it here} the
  pair of truncated traces $\overline{(C, 
    M)}_m$ and $\overline{(C, M')}_m$ is also in the set if $m < n$ \bcp{or
    $n = \infty$}.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.

\item {\em as in noninterfence:}

  For each pair of traces in the hyperproperty, if the initial machine
  states plus contour are variants, then the observervations of the
  two traces coincide.

\bcp{It feels like something is missing here: This definition seems to be
  requiring that secret data never affect observations, but our tester is
  ensuring something more: that inaccessible locations are not {\em changed}
(at least without also changing their tag to make them accessible).  Where
  is that condition being imposed?}
\leo{It's not - I just went by the definition of (traditional) noninterference
  you had and repeated that. I'm thinking about that now}
